---
name: Muhammad Aswan **Syahputra**
profilepic: "../img/aswan.jpg"
position: "Food Sensory and Sensometrics Consultant"
aboutme: "\"... how hard one finds it to learn something is a function of the intrinsic difficulty of the thing, the person's previous experience, preferred modes of thinking, etc., and how learning is approached.\" - John Fox"
address: "Agung Lestari Residence No B13, Jln. Somawinata, Ds. Tanimulya, Kec. Ngamprah, Kab. Bandung Barat, Jawa Barat"
phone: +62 822 3465 3816
www: aswansyahputra.com
email: "aswansyahputra@sensolution.id"
linkedin: aswansyahputra
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "37c871"
output: vitae::awesomecv
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Summary
I would like to recognize myself as a Food Data Scientist. I have expertise in Sensory Science with Food Technology background, passion in data analysis, and hobby in R programming and Shiny framework. As I always love Sensory Science, data analysis, and R programming, I then motivated to create of SenseHub: an integrated web application for sensory analyses.

# Education
```{r}
education <- read.csv("../data/education.csv")

education %>% 
  detailed_entries(
    what = what,
    when = when,
    with = with,
    where = where,
    why = why
  )
```

# Research Experience
```{r}
research <- read.csv("../data/research.csv")

research %>% 
  detailed_entries(
    what = event,
    when = when,
    with = topic,
    where = where,
    why = why
  )
```

# Projects
```{r}
project <- read.csv("../data/project.csv")

project %>% 
  brief_entries(
    what = what,
    when = when)
```

# Work Experience
```{r}
work <- read.csv("../data/work.csv")

work %>% 
  detailed_entries(
    what = what,
    when = when,
    with = with,
    where = where  )
```

# External Activity
```{r}
activity <- read.csv("../data/activity.csv")

activity %>% 
  brief_entries(
    what = what,
    when = when,
    with = with)
```

# Skills
```{r}
skill <- read.csv("../data/skill.csv")

skill %>% 
  brief_entries(
    what = what,
    when = when, 
    .protect = FALSE)
```
